\title{CSGames Qualifications 2020}
\author{Alexandre Frigon}
\date{\today}

\documentclass[12pt]{article}

\newcounter{i}

\begin{document}

\newcommand{\question}[1]{
    \stepcounter{i}
    \section*{Question \arabic{i}}
    #1
}

\section*{CSGames Qualifications 2020}

\subsection*{
    \begin{center}
        Theoretical Computing
    \end{center}
}

Use this Latex template to answer directly

\question {
    Name the data structure that fits the description:
    \begin{enumerate}
        \item Element search is in O(log n)
        \item Element insertion is in O(1)
        \item Element search is in O(1)
    \end{enumerate}
}

\question {
    Name a sorting algorithm that can complete in O(n)
}

\question {
    Can a sorting algorithm finish in O(log n) everytime without preprocessing the data?
}

\question {
    Explain what is a regular language?
}

\question {
    If we have $v = \{a, b\}$, give $v \star$.
}

\question {
    Given the regular expression $R = (ab*)*$, find an equivalent regular expression that only have a star height of 1 (no nested Kleene star). The allowed operations are union, concatenation and Kleene star.
}

\question {
    Is this equation true or false? justify.

    $$(\neg r \Rightarrow q) \vee \neg (q \vee s) \vee s \wedge q \wedge r \wedge \neg (t \wedge s) \Rightarrow (q \wedge \neg t) \vee r \wedge \neg s)$$
}

\question {
    If a language $L$ is regular, it's complement is also a regular language. true or false? justify.
}

\question {
    Explain in details the impact of a black box that could factorize products of prime numbers in polynomial time on the rsa cryptosystem.
}

\question {
    Explain the following regular expression:

    $$\epsilon \cup 0(0 \cup 1)\star \cup 1((0((1(0 \cup 1)(0 \cup 1)\star) \cup 0(0 \cup 1)\star)\star) \cup (1(0 \cup 1)(0 \cup 1)\star))\star$$
}

\question {
    Evaluate $\Omega = (\lambda x.xx)(\lambda x.xx)$
}

\question {
    Using Church encoding, evaluate $\lambda x. \lambda y.x(xy)$
}

\question {
    Explain, in your own words, Turing's proof of undecidability of the halting problem.
}

\question {
    Prove that $L = \{ xx : x \in \sum^\star \}$ is an irregular language.
}

\question {
    Prove $P = NP$
}

\end{document}

